---
title: Safety Science in Construction Management
author: Abdullah Alsharef
date: '2020-12-03'
slug: []
categories:
  - Construction Management
tags:
  - Safety
  - Risk
subtitle: ''
summary: ''
authors: []
lastmod: '2020-12-03T12:57:32-05:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---
# This is header 1
The biggest challenge when I opened the folders in the demo folder is naming of various files. It has made the modification very difficult because it’s hard to know and remember what you’re actually modifying. Here is an example about what I’m talking about.

The biggest challenge when I opened the folders in the demo folder is naming of various files. It has made the modification very difficult because it’s hard to know and remember what you’re actually modifying. Here is an example about what I’m talking about.
The biggest challenge when I opened the folders in the demo folder is naming of various files. It has made the modification very difficult because it’s hard to know and remember what you’re actually modifying. Here is an example about what I’m talking about.


The biggest challenge when I opened the folders in the demo folder is naming of various files. It has made the modification very difficult because it’s hard to know and remember what you’re actually modifying. Here is an example about what I’m talking about.

## Next Header 


The biggest challenge when I opened the folders in the demo folder is naming of various files. It has made the modification very difficult because it’s hard to know and remember what you’re actually modifying. Here is an example about what I’m talking about.


# Header 2

## Next Level

some R code


```{r}
head(mtcars)

plot(mtcars$mpg, mtcars$disp)
```



```{r}
plot(mtcars)

summary(mtcars)
```






































